---
title       : Child Height Prediction
subtitle    : Developing Data Products Course Project
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---page 2
## Data Set

This preditcion algorithm uses galton data set in the library UsingR. 
```{r}
library(UsingR)
summary(galton)
```

---page 3
## Build the model

A linear regression model is fit to the data.
```{r}
fit<-lm(child~parent, data=galton)
summary(fit)
```


---page 4
## Prediction

The prediction model takes father height and mother height as input and convert them to parent height. Then parent height is used to predict child height.
As the used data set has parent height range from 64 to 73, the prediction works when parent height is within that range.

```{r}
ChildHeight<-function(father,mother){
    as.vector(predict(fit,data.frame(parent=mean(c(father,1.08*mother)))))
    }
```

---page 5
## Residual plot and model diagnose

```{r}
par(mfrow=c(2,2))
plot(fit)
```


