---
title       : Child Height Prediction
subtitle    : Developing Data Products Course Project
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---page 2

## The idea

- How tall your child will be when they grow up?
- The height of a person is determined by a combination of many factors, such as genetics, nutrition, etc. 
- However, genetics has been suggested by some studies to contribute 60%-80% to a person's height.
- We have built a model to estimate child height based on parent height.

---
## Data Set

This preditcion algorithm uses galton data set in the library UsingR. 
```{r}
library(UsingR)
summary(galton)
```

---page 3
## Build the model

A linear regression model is fit to the data.
```{r}
fit<-lm(child~parent, data=galton)
summary(fit)
```


---page 4
## Prediction

- The prediction model takes father height and mother height as input and convert them to parent height. 
- Then parent height is used to predict child height.
- As the used data set has parent height range from 64 to 73, the prediction works when parent height is within that range.
- Go to the websit [here](https://karenlyz.shinyapps.io/HW_Project/) to try out the application.


